\mutagen: Coverage-Guided, Property-Based Testing using Exhaustive Structure-Preserving Mutations

### 2021-09-03 papers/icse22/main.tex
Section 5 pass

We evaluated the performance of \mutagen using two case studies.
%
The first one is a simple abstract stack machine that enforces
\emph{noninterference} \cite{goguen1982security} using runtime checks.
%
Its implementation was proven correct by \citeauthor{10.1145/2578855.2535839}
\citeyearpar{10.1145/2578855.2535839} in Coq, and subsequently degraded by
systematically introducing 20 bugs on its enforcing mechanism.
%
\citeauthor{lampropoulos2019coverage} used this case study to compare \fuzzchick
against RPBT using na\"ive- and hand-tuned random generators.
%
Here, we replicate their results and compare them against our tool.
%
Worth mentioning, we translated this case study into Haskell in order to run
\mutagen on its test suite.

The second case study aims to evaluate \mutagen in a realistic scenario, and
targets \textit{haskell-wasm} \cite{haskellwasm}, an existing WebAssembly engine
of industrial strength written in Haskell.
%
%
Sadly, comparing \mutagen with \fuzzchick on this case study has been out of the
scope of this work, since porting \textit{haskell-wasm} into Coq, and later
adapting our test suite to work with \fuzzchick requires a subtantial effort.
%
Instead, we compare \mutagen against a traditional RPBT approach, evaluating its
effectiveness versus the relative overhead of the code instrumentation used by
our tool.

>>>>

We evaluated the performance of \mutagen using two case studies.
%
The first one is a simple abstract stack machine that enforces
\emph{noninterference} \cite{goguen1982security} using runtime checks.
%
Its implementation was proven correct by \citeauthor{10.1145/2578855.2535839}
\citeyearpar{10.1145/2578855.2535839} in Coq, and subsequently degraded by
systematically introducing 20 bugs on its enforcing mechanism.
%
\citeauthor{lampropoulos2019coverage} used this case study to compare \fuzzchick
against RPBT using na\"ive- and hand-tuned random generators.
%
Here, we replicate their results and compare them against our tool.
%
Worth mentioning, we reimplemented this case study from scratch in Haskell in
order to run \mutagen on its test suite.

The second case study aims to evaluate \mutagen in a realistic scenario, and
targets \textit{haskell-wasm} \cite{haskellwasm}, an existing WebAssembly engine
of industrial strength.
%
%
Sadly, comparing \mutagen with \fuzzchick on this case study has been out of the
scope of this work, since porting \textit{haskell-wasm} into Coq, and later
adapting our test suite to work with \fuzzchick requires a subtantial effort.
%
Instead, we compare \mutagen against a traditional RPBT approach, evaluating its
effectiveness versus the relative overhead of the code instrumentation used by
our tool.
